Supplementary Material for Asymmetry paper

### 2020-05-21 Supplementary/Sup_mat.Rmd
tweak so model code displays

@@

## Experiment 1: Hoop Size
```{r run model Hoop Size, include = F, echo = F, cache = TRUE}
# load model data 
load("../Analyses/Experiment_3_Hoop_size/data/model_data")

>>>>

```{r, echo - FALSE}
# load model data 
load("../Analyses/Experiment_3_Hoop_size/data/model_data")

@@

## Experiment 1: Hoop Size

### Prior Predictive Check

First, we will check that our priors are sensible!

```{r run-model-hoop-size-priors, echo = T, cache = TRUE}

# run model
Hoop_size_m1 <- brm(norm_dist2 ~ norm_hoop_pos + (norm_hoop_pos|participant), 
          data = model_data,
          family = "beta",
          prior = c(set_prior("student_t(3,0,3)", class = "b")),
          cores = 1,
          chains = 1,
          iter = 2000,
          warmup = 1000,
          sample_prior = "only")
```

### Conditioning on the data

```{r run-model-Hoop-size, include = F, echo = F, cache = TRUE}
